# 1st Project: 5-Year Trend Table {-}

A trend table containing percent-change-data of different variables for 54 individual states across 2015-2020 time period:

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#write.csv(Trend_Data_2.0, "first_project.csv")
first_project <- read_excel("Data/1st_project/first_project.xlsx")

first_project <- first_project %>%
  mutate(Award_Pct_Change = as.numeric(Award_Pct_Change),
         PIT_Pct_Change = as.numeric(PIT_Pct_Change),
         PerCap_Pct_Change = as.numeric(PerCap_Pct_Change),
         Chronic_Pct_Change = as.numeric(Chronic_Pct_Change),
         MI_Pct_Change = as.numeric(MI_Pct_Change),
         SUD_Pct_Change = as.numeric(SUD_Pct_Change)
         )

#kable(first_project[1:324,])

data1 <- SharedData$new(first_project)
bscols(
  widths = c(3, NA),
  list(
    filter_select("State", "State", data1, ~State),
    filter_slider("Year", "Year", data1, ~Year, ticks = FALSE, sep = FALSE)
    ),
reactable(data1, searchable = TRUE, showPageSizeOptions = TRUE, defaultPageSize = 10, highlight = TRUE, bordered = TRUE, height = 700,
          columns = list(
          `Award Amount` = colDef(format = colFormat(prefix = "$", separators = TRUE)),
          Per_Capita = colDef(name = "Per Capita", format = colFormat(prefix = "$", separators = TRUE, digits = 2)),
          Award_Pct_Change = colDef(name = "Award %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          PIT_Pct_Change = colDef(name = "PIT %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          PerCap_Pct_Change = colDef(name = "Per Capita %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          Chronic_Pct_Change = colDef(name = "Chronic %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          MI_Pct_Change = colDef(name = "MI %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          SUD_Pct_Change = colDef(name = "SUD %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          `Sheltered Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Unsheltered Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Overall Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Overall Chronically Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Severely Mentally Ill` = colDef(format = colFormat(separators = TRUE)),
          `Chronic Substance Abuse` = colDef(format = colFormat(separators = TRUE))
          )))
```


## State Average {-}

A trend table containing total sum of percent-change-data all years for 54 individual states:

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#write.csv(Trend_Data_2.0_State, "first_project_State.csv")
first_project_State <- read_excel("Data/1st_project/first_project_State.xlsx")

first_project_State <- first_project_State %>%
  mutate(Award_Pct_Change = as.numeric(Award_Pct_Change),
         PIT_Pct_Change = as.numeric(PIT_Pct_Change),
         PerCap_Pct_Change = as.numeric(PerCap_Pct_Change),
         Chronic_Pct_Change = as.numeric(Chronic_Pct_Change),
         MI_Pct_Change = as.numeric(MI_Pct_Change),
         SUD_Pct_Change = as.numeric(SUD_Pct_Change)
         )

#kable(first_project_State[1:54,])

data2 <- SharedData$new(first_project_State)
bscols(
  widths = c(3, NA),
  list(
    filter_select("State", "State", data2, ~State)
    ),
reactable(data2, searchable = TRUE, showPageSizeOptions = TRUE, defaultPageSize = 10, highlight = TRUE, bordered = TRUE, height = 500,
          columns = list(
          `Award Amount` = colDef(format = colFormat(prefix = "$", separators = TRUE)),
          Award_Pct_Change = colDef(name = "Award %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          PIT_Pct_Change = colDef(name = "PIT %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          PerCap_Pct_Change = colDef(name = "Per Capita %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          Chronic_Pct_Change = colDef(name = "Chronic %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          MI_Pct_Change = colDef(name = "MI %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          SUD_Pct_Change = colDef(name = "SUD %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2))
          )))
```


## Nation Average {-}

A trend table containing total sum of different variables and % change of those variables of all states for each year across 2015-2020:

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#write.csv(Trend_Data_2.0_Nation, "first_project_Nation.csv")
first_project_Nation <- read_excel("Data/1st_project/first_project_Nation.xlsx")

first_project_Nation <- first_project_Nation %>%
  mutate(Award_Pct_Change = as.numeric(Award_Pct_Change),
         PIT_Pct_Change = as.numeric(PIT_Pct_Change),
         PerCap_Pct_Change = as.numeric(PerCap_Pct_Change),
         Chronic_Pct_Change = as.numeric(Chronic_Pct_Change),
         MI_Pct_Change = as.numeric(MI_Pct_Change),
         SUD_Pct_Change = as.numeric(SUD_Pct_Change)
         )

#kable(first_project_Nation[1:6,])

data3 <- SharedData$new(first_project_Nation)

reactable(data3, searchable = TRUE, showPageSizeOptions = TRUE, defaultPageSize = 10, highlight = TRUE, bordered = TRUE,
          columns = list(
          `Award Amount` = colDef(format = colFormat(prefix = "$", separators = TRUE)),
          Per_Capita = colDef(name = "Per Capita", format = colFormat(prefix = "$", separators = TRUE, digits = 2)),
          Award_Pct_Change = colDef(name = "Award %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          PIT_Pct_Change = colDef(name = "PIT %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          PerCap_Pct_Change = colDef(name = "Per Capita %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          Chronic_Pct_Change = colDef(name = "Chronic %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          MI_Pct_Change = colDef(name = "MI %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          SUD_Pct_Change = colDef(name = "SUD %Change", format = colFormat(suffix = "%", separators = TRUE, digits = 2)),
          `Sheltered Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Unsheltered Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Overall Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Overall Chronically Homeless` = colDef(format = colFormat(separators = TRUE)),
          `Severely Mentally Ill` = colDef(format = colFormat(separators = TRUE)),
          `Chronic Substance Abuse` = colDef(format = colFormat(separators = TRUE))
          ))
```




```{r include=FALSE, eval=FALSE, warning=FALSE, message=FALSE}

# 5-Year Trend Table (Inflation Adjusted) {-}

All values of "Award Amount" has been adjusted using CPI Index with 2015 as the base-year dollar value. This change will also influence the "Per Capita" column. A trend table containing percent-change-data for 54 individual states across 2015-2020 time period:


#write.csv(Trend_Data_2.0_Înflation, "first_project_Inflation.csv")
first_project_Inflation <- read_excel("Data/1st_project/first_project_Inflation.xlsx")

kable(first_project_Inflation[1:324,])



## State Average {-}

A trend table containing total sum of percent-change-data all years for 54 individual states:

#write.csv(Trend_Data_2.0_Inflation_State, "first_project_Inflation_State.csv")
first_project_Inflation_State <- read_excel("Data/1st_project/first_project_Inflation_State.xlsx")

kable(first_project_Inflation_State[1:54,])



## Nation Average {-}

A trend table containing total sum of percent-change-data all states for each year across 2015-2020:

#write.csv(Trend_Data_2.0_Inflation_Nation, "first_project_Inflation_Nation.csv")
first_project_Inflation_Nation <- read_excel("Data/1st_project/first_project_Inflation_Nation.xlsx")

kable(first_project_Inflation_Nation[1:6,])


```



